### 2018-02-17 doc/esm.Rmd
ref to results dataframe

```{r table_tagfa}
table_tagfa(caption = tab_tagfa)
```

```{r table_gee}
table_gee_main(gee_unadj_df, caption = tab_gee_unadj)
table_gee_main(gee_adj_df, caption = tab_gee_adj)
```

>>>>

```{r table_tagfa}
table_tagfa(project_data, caption = tab_tagfa)
```

```{r table_gee}
table_gee_main(gee_results$unadj, caption = tab_gee_unadj)
table_gee_main(gee_results$adj, caption = tab_gee_adj)
```
